\bf Looking at Non-Linear Dimension Reductions as Models in the Data Space

### 2024-10-17 paper.tex
Added PaCMAP model for two C-shaped data
Updated Figure 2 title

\caption{\label{fig-two-curvy-true-proj}Two views of the true model
(blue lines) in \(2\text{-}D\) projections from \(7\text{-}D\), for the
two C-shaped clusters data (grey points). The data is spread along the
non-linear shaped clusters, and does not vary much from the curves. The
\textbf{langevitour} software is used to view the data with a tour, and
the full video is available at \textless\textgreater.}

@@

{\centering \includegraphics[width=1\textwidth,height=0.9\textheight]{paper_files/figure-pdf/best-fit-umap-tsne-1.pdf}

>>>>

\caption{\label{fig-two-curvy-true-proj}Two views of the true model
(blue lines) in \(2\text{-}D\) projections from \(7\text{-}D\), for the
two C-shaped clusters data (grey points). In one C-shaped cluster, the
data is spread throughout the cluster, while in the other C-shaped
cluster, the data is concentrated more in one corner of the cluster. The
\textbf{langevitour} software is used to view the data with a tour, and
the full video is available at \textless\textgreater.}

@@

{\centering \includegraphics[width=1\textwidth,height=0.9\textheight]{paper_files/figure-pdf/best-fit-umap-tsne-pacamp-1.pdf}
